%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Yathartha}{Joshi}{ \urlstyle{same}\href{http://yathartha22.github.io}{yathartha22.github.io} \\
\href{mailto:yathartha32@gmail.com}{yathartha32@gmail.com} | +91 8126689890 | +91 9756058421
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Netaji Subhas \\ University of Technology}
\descript{M.Tech in Computer Science}
\location{2019-21 | New Delhi, India}
\location{Aggr. CGPA: 7.90}
\sectionsep

\subsection{BTKIT, Dwarahat}
\descript{Bachelor of Technology in Computer Science and Engineering}
\location{2014-18 | Uttarakhand, India}
\location{Percentage: 73.26}
\sectionsep

\subsection{Nirmala Convent \\Sr. Sec. School}
\location{Grad. May 2014|  Uttarakhand, India}
\location{Percentage: 92.80}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Facebook:// \href{https://www.facebook.com/yathartha.joshi.399}{\bf yathartha} \\
Github:// \href{https://github.com/Yathartha22}{\bf yathartha22} \\
LinkedIn://  \href{https://www.linkedin.com/in/yathartha-joshi-962701123}{\bf yatharthajoshi} \\
Twitter://  \href{https://twitter.com/yatharthajoshi2}{\bf @yatharthajoshi2} \\
GeeksForGeeks://  \href{https://auth.geeksforgeeks.org/user/YatharthaJoshi/}{\bf Yathartha-Joshi} \\
StackoverFlow://  \href{https://stackoverflow.com/users/6446166/yathartha-joshi}{\bf Yathartha-Joshi} \\
Hackerearth://  \href{https://www.hackerearth.com/@yathartha32}{\bf yathartha32} \\
Hackerrank://  \href{https://www.hackerrank.com/yathartha}{\bf yathartha}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
C \textbullet{}   C++ \textbullet{} Python \textbullet{} Java \\
\textbullet{} Ruby
\subsection{Operating Systems}
Linux \textbullet{} Windows
\subsection{Web/Database Based \\ Technologies}
HTML \textbullet{} CSS \textbullet{} JavaScript \\
\textbullet{} Php \textbullet{} MySQL
\subsection{Tools and Framework}
Django \textbullet{} Bootstrap  \textbullet{} Git \\
\textbullet{} Rails \textbullet{} pandas \\
\textbullet{} scikit-learn \textbullet{} numpy \\
\textbullet{} matplotlib \textbullet{} nltk \textbullet{} keras \\
\textbullet{} tensorflow \textbullet{} PyTorch
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

% \runsubsection{HackerRank | SDE Intern}
% \descript{| January 2021-Present}
% \vspace{\topsep}
% \begin{tightemize}
% \item Currently working on their product Hexagon, which provides a
% way for companies to analyze their employees.
% \end{tightemize}
% \sectionsep

\runsubsection{HackerRank | Software Developer Intern}
\descript{| january 2021-Present}
\vspace{\topsep}
\begin{tightemize}
\item Currently working on building their product hexagon, which helps companies
analyse their employees.
\item Also working with the Rails migration team.
\end{tightemize}
\sectionsep

\runsubsection{LCS2, IIITD | Research Intern}
\descript{| December 2020-Present}
\vspace{\topsep}
\begin{tightemize}
\item Currently working on building Web tool for Information Cascading on Twitter data.
\item Scraping tweet data and serving the model are primary tasks.
\end{tightemize}
\sectionsep

\runsubsection{Google Summer of Code  | 2020 | 2019 | Mentor}
\descript{| Mentor for SymPy Project}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Mentor for improving the Number Theory module in SymPy.
\item Mentor for the development of Physics module in SymPy
\item Mentor for the development of solvers in SymPy
\href{https://summerofcode.withgoogle.com/projects/#5233982339284992}{[1]}
\href{https://summerofcode.withgoogle.com/archive/2019/projects/5351176374059008/}{[2]}
\href{https://summerofcode.withgoogle.com/archive/2019/projects/4722757948932096/}{[3]}
\end{tightemize}
\sectionsep

\runsubsection{Google Summer of Code 2018 | Student}
\descript{| SymPy }
\location{May 2018 – August 2018}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Improved Mathematical robustness of new solvers module.
\item Implemented Transcendental Equation solver for solvers module
\item Set Theory, Linear Algebra
\href{https://summerofcode.withgoogle.com/archive/2018/projects/6261947964063744/}{[1]}
\end{tightemize}
\sectionsep

\runsubsection{KiloByte Technologies}
\descript{| Python/Django Intern |}
\location{June 2017 – July 2017 | Vaishali, India}
\begin{tightemize}
\item Worked on creating scripts for scrapping data. Also had a learning exprience in creating a Blogging application entirely
in Django.
\href{https://github.com/Yathartha22/farcon_image_scrapper}{[1]}
\href{https://github.com/Yathartha22/quotesBot}{[2]}
\href{https://github.com/Yathartha22/nasa}{[3]}
\href{https://github.com/Yathartha22/myblog}{[4]}
\end{tightemize}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Story Generator | Neural Text Generation}
\location{| October 2020 - December 2020}
Using bidirectional LSTM to create a story generator, where meaningful words are generated by the model.
Wor2vec is used for better word prediction.
\sectionsep

\runsubsection{Job Recommender System}
\location{| March 2020 - May 2020}
Worked on creating a recommender system that will suggest 3-4 job profiles as per the candidate's resume.
\href{https://github.com/Yathartha22/Job-Recommender-System}{[1]}
\sectionsep

\runsubsection{Notification Application for Colleges}
\descript{| Backend Developer}
Worked with another teammate on creating an Android application for creating, publishing and viewing notifications related to college.
\href{https://github.com/Yathartha22/notices-api}{[1]}
\href{https://drive.google.com/file/d/0B5EALEdIC0ktZ1JQRUhCdjZ1Z1NxSkVHT3Mwb3Rab3JtRmQ0/view?usp=sharing}{[2]}
\sectionsep

% \runsubsection{ColoredCow BootCamp} \\
% Attended a Bootcamp organised by ColoredCow, where I worked on developing a simple Php application considering the phases of
% Software Development Life Cycle.
% \href{https://github.com/Yathartha22/codetrek}{[1]}
% \href{https://drive.google.com/file/d/0B5EALEdIC0ktY2thRjhxbUtrU1FDWERfYnR3aEd3QVZyVzVr/view?usp=sharing}{[2]}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
% 2019	    & Graduate Aptitude test (GATE) qualified\\
2017		& \href{https://drive.google.com/file/d/0B5EALEdIC0ktNFRBOWhNZk4wcTdnY253bnJNQVY0dmZCRkEw/view?usp=sharing}{AIR 14 in IEEE Xtreme 11.0}\\
2016		& \href{https://drive.google.com/file/d/0B5EALEdIC0ktNFRBOWhNZk4wcTdnY253bnJNQVY0dmZCRkEw/view?usp=sharing}{AIR 22 in IEEE Xtreme 10.0}\\
% 2016		& Qualified Google Code Jam Qualifiers.\\
% 2013	 	& Head Boy of the school.

\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications} 
% \renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
